Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-19 paper/paper.tex
Conclude

\usepackage{microtype}                 % typographic perfection
\usepackage{complexity}                % \P, \NP etc
\usepackage{tikz}                      % For pretty pictures
\usepackage{amsmath}                   % \operatorname
\usepackage{amssymb}                   % \triangledown
\usepackage{hyperref}                  % clicky links
\usepackage{cleveref}                  % no need to type Figure etc
\usepackage{gnuplot-lua-tikz}          % graphs
\usepackage[ruled,vlined]{algorithm2e} % algorithms (after cleverref!)
\usepackage{cite}                      % automatically sort mass cites
\usepackage[bottom]{footmisc}          % fix footnote + bottom figure on same page
\usepackage{placeins}                  % \FloatBarrier

@@

We have seen that a modern clique algorithm can perform competitively for maximum common subgraph
problems, particularly when edge labels are involved.

We believe there is further scope for tailoring clique algorithms for association graphs.
Specialised inference, association-aware bound function. Treating the first branch specially, since
it will eliminate so much of the search space \cite{DBLP:conf/cocoon/SutersAZSSL05}.

For CP models for the connected version of the problem, we saw the benefits of combining
conventional filtering with a special branching rule. Using a branching rule for correctness, rather
than simply as an ordering heuristic, is unconventional and does not cleanly fit into the
abstractions used by toolkits.

We looked only at single-threaded versions of these algorithms. Maximum clique algorithms have been
extended for thread-parallel search
\cite{DBLP:journals/algorithms/McCreeshP13,DBLP:journals/jcisd/DepolliKRTJ13,DBLP:journals/cor/SegundoLP16}.
In particular, EHPs \cite{DBLP:journals/topc/McCreeshP15}. On the CP side, decomposition \cite{DBLP:conf/ictai/MinotNS15}.

We haven't discussed partial or weighted subgraphs, or strongly connected directed.

Symmetries. Dynamic.

Better instances.

@@

\FloatBarrier % looks better this way...
\bibliographystyle{splncs}
\bibliography{paper}

>>>>

\usepackage{microtype}                 % typographic perfection
\usepackage{complexity}                % \P, \NP etc
\usepackage{tikz}                      % For pretty pictures
\usepackage{amsmath}                   % \operatorname
\usepackage{amssymb}                   % \triangledown
\usepackage{hyperref}                  % clicky links
\usepackage{cleveref}                  % no need to type Figure etc
\usepackage{gnuplot-lua-tikz}          % graphs
\usepackage[ruled,vlined]{algorithm2e} % algorithms (after cleverref!)
\usepackage{cite}                      % automatically sort mass cites
\usepackage[bottom]{footmisc}          % fix footnote + bottom figure on same page

@@

We have seen that a modern clique algorithm can perform competitively for maximum common subgraph
problems, particularly when edge labels are involved.  We believe there is further scope for
tailoring clique algorithms for association graphs, including specialised inference, a bound
function which is aware that it is working on an association graph, and better initial vertex
orderings. Treating the first branch specially may also be beneficial, since the first branch has an
unusually large effect on the search space with association graphs
\cite{DBLP:conf/cocoon/SutersAZSSL05}.

For CP models, using a branching rule for correctness, rather than simply as an ordering heuristic,
is unconventional and does not cleanly fit into the abstractions used by toolkits. However, we saw
that combining conventional filtering and the special branching rule was beneficial.

We looked only at single-threaded versions of these algorithms. Maximum clique algorithms have been
extended for thread-parallel search
\cite{DBLP:journals/algorithms/McCreeshP13,DBLP:journals/jcisd/DepolliKRTJ13,DBLP:journals/cor/SegundoLP16},
and in particular, work stealing strategies designed to eliminate exceptionally hard instances by
forcing diversity at the top of search \cite{DBLP:journals/topc/McCreeshP15} could be beneficial in
eliminating some of the rare cases where the clique algorithm is many orders of magnitude worse than
the CP models. On the CP side, the focus for parallelism has been on decomposition
\cite{DBLP:conf/ictai/MinotNS15}, rather than fully dynamic work stealing---it would be interesting
to compare these approaches.

Finally, we intend to investigate larger and more diverse sets of instances, and other variants of
the problem. We have yet to investigate partial or weighted graphs. Nor have we considered strongly
connected common subgraphs---this would make the branching approach impossible, and filtering would
be much more complicated. From the datasets we selected, there appears to be little scope for
per-instance algorithm selection, but other families of input data could lead to a different
conclusion.

@@

\bibliographystyle{splncs}
\bibliography{paper}
